MSE for rank_1 simulation

### 2018-01-27 analysis/MSErank1sim.Rmd
Files commited by wflow_commit.

```{}
library(PMA)
library(flashr2)
library(ssvd)
source("../Rfunction.R")
L_se = c( 0.25, 0.5, 1, 2, 4)
L_pi = c(1, 1,1,1,1)
L_pi = L_pi / sum(L_pi)
N = 200
P = 300
Data = datamaker(N,P,L_pi,L_se,0.7,c(1),c(1),1,sqrt(16))
# Data = datamaker(N,P,L_pi,L_se,0.1,c(1),c(1),1,sqrt(1))  sparse case
# Data = datamaker(N,P,L_pi,L_se,1.0,c(1),c(1),1,sqrt(1))  dense case
RMSE = rep(NA,6)
RMSE[1] = PMA.wrapper(Y_data)
RMSE[2] = flash.wrapper(Y_data)
RMSE[3] = SFA.wrapper(Y_data, K = 1)
RMSE[4] = SFAmix.wrapper(Y_data,K = 1)
RMSE[5] = SVD.wrapper(Y_data)
RMSE[6] = SSVD.wrapper(Y_data)
saveRDS(result, "./output.rds")
```

@@

@@

```{r}
plot_res = function(output,title = "data",legend_position = "none", methods_name){
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(methods_name, each = N)
  df = data.frame(RRMSE_diff = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RRMSE_diff, color=Method)) +
  geom_boxplot()+
  # geom_violin()+
  ggtitle(title) +  theme_bw()+
    theme(legend.position= legend_position, legend.text=element_text(size=10),
          axis.text.y = element_text(size =12),
          axis.text.x = element_text(size =12,angle = 45, hjust = 1))
  p
}
library(ggplot2)
```

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_sparse.rds")
colnames(sparse_res) = c("PMD.cv2","flash","SFA","flash.pn","SVD","SSVD","PMD.cv1","SFAmix","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
methods_name = colnames(sparse_diff)
p1 = plot_res(sparse_diff,title = "Difference from FLASH result (90% zeros)",methods_name = methods_name)
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p1_cut = plot_res(sparse_diff[-22,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (90% zeros)",methods_name = methods_name)
```

@@

methods_name = colnames(sparse_diff)
p2 = plot_res(sparse_diff,title = "Difference from FLASH result (30% zeros)",methods_name = methods_name)
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p2_cut = plot_res(sparse_diff[,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (30% zeros)",methods_name = methods_name)
```

@@

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_dense.rds")
colnames(sparse_res) = c("PMD.cv2","flash","SFA","flash.pn","SVD","SSVD","PMD.cv1","SFAmix","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
# p3 = plot_res(sparse_diff,"Difference from FLASH result (0% zeros)")
methods_name = colnames(sparse_diff)
p3 = plot_res(sparse_diff,title = "Difference from FLASH result (0% zeros)",methods_name = methods_name)
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p3_cut = plot_res(sparse_diff[,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (0% zeros)",methods_name = methods_name)
```

>>>>

```{}
library(PMA)
library(flashr2)
library(ssvd)
source("../Rfunction.R")
L_se = c( 0.25, 0.5, 1, 2, 4)
L_pi = c(1, 1,1,1,1)
L_pi = L_pi / sum(L_pi)
N = 200
P = 300
Data = datamaker(N,P,L_pi,L_se,0.7,c(1),c(1),1,sqrt(16))
# Data = datamaker(N,P,L_pi,L_se,0.1,c(1),c(1),1,sqrt(1))  sparse case
# Data = datamaker(N,P,L_pi,L_se,1.0,c(1),c(1),1,sqrt(25))  dense case
RMSE = rep(NA,6)
RMSE[1] = PMA.wrapper(Y_data)
RMSE[2] = flash.wrapper(Y_data)
RMSE[3] = SFA.wrapper(Y_data, K = 1)
RMSE[4] = SFAmix.wrapper(Y_data,K = 1)
RMSE[5] = SVD.wrapper(Y_data)
RMSE[6] = SSVD.wrapper(Y_data)
saveRDS(result, "./output.rds")
```

@@

## get the result

@@

```{r}
plot_res = function(output,title = "data",legend_position = "none", methods_name,myColors){
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(methods_name, each = N)
  df = data.frame(RRMSE_diff = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RRMSE_diff, color=Method)) +
  geom_boxplot()+
  # geom_violin()+
  ggtitle(title) +  theme_bw()+ scale_color_manual(values=myColors)+
    theme(legend.position= legend_position, legend.text=element_text(size=10),
          axis.text.y = element_text(size =12),
          axis.text.x = element_text(size =12,angle = 45, hjust = 1))
  p
}
library(ggplot2)
```

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_sparse.rds")
colnames(sparse_res) = c("PMD.cv2","flash","SFA","flash.pn","SVD","SSVD","PMD.cv1","SFAmix","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
methods_name = colnames(sparse_diff)
fill_color = c("red","yellow3", "springgreen", "springgreen3", "cyan","cyan3", "deepskyblue","violet","purple")
p1 = plot_res(sparse_diff,title = "Difference from FLASH result (90% zeros)",
              methods_name = methods_name, myColors = fill_color)
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p1_cut = plot_res(sparse_diff[-22,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (90% zeros)",methods_name = methods_name,myColors = fill_color[c(1,2,3,4,5,7,9)])
```

@@

methods_name = colnames(sparse_diff)
p2 = plot_res(sparse_diff,title = "Difference from FLASH result (30% zeros)",methods_name = methods_name,myColors = fill_color)
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p2_cut = plot_res(sparse_diff[,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (30% zeros)",methods_name = methods_name,myColors = fill_color[c(1,2,3,4,5,7,9)])
```

@@

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_dense.rds")
colnames(sparse_res) = c("PMD.cv2","flash","SFA","flash.pn","SVD","SSVD","PMD.cv1","SFAmix","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
# p3 = plot_res(sparse_diff,"Difference from FLASH result (0% zeros)")
methods_name = colnames(sparse_diff)
p3 = plot_res(sparse_diff,title = "Difference from FLASH result (0% zeros)",methods_name = methods_name,myColors = fill_color )
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p3_cut = plot_res(sparse_diff[,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (0% zeros)",methods_name = methods_name,myColors = fill_color[c(1,2,3,4,5,7,9)])
```
